Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-13 manuscript/manuscript.tex
Minor changes to linear density text

\begin{table}
\caption{
    Description of the tesseroid collections used to build a spherical shell and
    characterize the accuracy of the numerical integration.
    The first three columns describe the shapes of the tesseroid collections: each one
    specifies the number of tesseroids on the corresponding dimension (radial,
    latitudinal, longitudinal).
    The last two columns specify the latitudinal and longitudinal size of each
    tesseroid that compose the spherical shell model.
    For each collection, we define four spherical shell models with an outer radius
    equal to the mean Earth radius (6378.137 km) and the inner radius determined by the
    following thicknesses: 100m, 1km, 10km, 100km and 1000km.
}
\label{tab:tess-collections}
\begin{tabular}{cccccc}
    Radial & Latitudinal & Longitudinal  & Total tesseroids & $L_\phi$ & $L_\lambda$
    \\ \hline
    1 & 1  & 2  & 2   & 180$^\circ$ & 180$^\circ$ \\
    1 & 6  & 12 & 72  &  30$^\circ$ &  30$^\circ$ \\
    1 & 12 & 24 & 288 &  15$^\circ$ &  15$^\circ$ \\
    1 & 18 & 36 & 648 &  10$^\circ$ &  10$^\circ$ \\
\end{tabular}
\end{table}

@@

In order to compare the numerical results with the analytical solution we
must build spherical shell models made of tesseroids.
These shell models are determined by their inner and outer radii and by the collection
of tesseroids used to build the shell.
For this analysis we have chosen to set the outer radii of every shell model equal to
the mean Earth radius (6378.137 km), while the inner radius is determined by the desired
thickness of the shell.
We choose  different values of shell thickness (100m, 1km, 10km, 100km and 1000km) in
order to account for different computation scenarios.
Furthermore, we propose different tesseroids collections to build the shell model by
regularly splitting it along the longitudinal and latitudinal directions.
Each collection, described in Table~\ref{tab:tess-collections}, is composed by
a different number of tesseroids, i.e.~with tesseroids of different sizes.
Finally, for each collection we build a shell model with the thicknesses
previously described, giving a total of 20 different shell models.

>>>>

\begin{table}
\caption{
    Description of the tesseroid collections used to build a spherical shell and
    characterize the accuracy of the numerical integration.
    The first three columns describe the shapes of the tesseroid collections: each one
    specifies the number of tesseroids on the corresponding dimension (radial,
    latitudinal, longitudinal).
    The last two columns specify the latitudinal and longitudinal size of each
    tesseroid that compose the spherical shell model.
    For each collection, we define five spherical shell models with an outer radius
    equal to the mean Earth radius (6378.137 km) and the inner radius determined by the
    following thicknesses: 100m, 1km, 10km, 100km and 1000km.
    This makes a total of 20 shell models combining tesseroids collections and
    thicknesses.
}
\label{tab:tess-collections}
\begin{tabular}{cccccc}
    Radial & Latitudinal & Longitudinal  & Total tesseroids & $L_\phi$ & $L_\lambda$
    \\ \hline
    1 & 1  & 2  & 2   & 180$^\circ$ & 180$^\circ$ \\
    1 & 6  & 12 & 72  &  30$^\circ$ &  30$^\circ$ \\
    1 & 12 & 24 & 288 &  15$^\circ$ &  15$^\circ$ \\
    1 & 18 & 36 & 648 &  10$^\circ$ &  10$^\circ$ \\
\end{tabular}
\end{table}

@@

In order to compare the numerical results with the analytical solution we
must build spherical shell models made of tesseroids.
These shell models are determined by their inner and outer radii and by the collection
of tesseroids used to build the shell.
For this analysis we have chosen to set the outer radii of every shell model equal to
the mean Earth radius (6378.137 km), while the inner radius is determined by the desired
thickness of the shell.
We choose  different values of shell thickness (100m, 1km, 10km, 100km and 1000km) in
order to account for different computation scenarios.
Furthermore, we propose different tesseroids collections to build the shell model by
regularly splitting it along the longitudinal and latitudinal directions.
Each collection, described in Table~\ref{tab:tess-collections}, is composed by
a different number of tesseroids, i.e.~with tesseroids of different sizes.
Finally, combining these collections and the thicknesses we obtain 20 different shell
models.
